---
title: "Practical Machine Learning Course Project"
author: "Victor Yim"
date: "4 March 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Loading Library
We need the caret library and also the randomForest library for faster performance in fitting rf model.
```{r message=FALSE, results='hide'}
library(caret)
library(randomForest)
```

## Course Project Summary
1. First I load the training data data.
```{r data}
setwd("~/Documents/R/praticalMachineLearning")
data<-read.csv("pml-training.csv")
case<-read.csv("pml-testing.csv")
```
2. I examine the dataset. There are 160 variables. By quickly looking at the data and the label of the variables, I decide to use the x,y,z measurements of the 4 gyrometers and accelerometers, a total of 24 features to fit the model.
```{r feature_selection}
gyros<-grep("^gyros",names(data))
accel<-grep("^accel",names(data))
select_feature<-c(gyros,accel,160) # with the outcome
```
Creating Training/Testing Sets
``` {r split_dataset}
inTrain <- createDataPartition(y=data$classe,p=0.75, list=FALSE)
training <- data[inTrain,select_feature]
testing <- data[-inTrain,select_feature]
```
3. I tried random forest and it yields a pretty good accuracy of 97%:
```{r fit}
# Fit model using random forrest
modelFit<-randomForest(classe~.,method="rf",data=training)
# Valid the model with the testing data
confusionMatrix(testing$classe,predict(modelFit,testing))$overall[1]
```
4. I then tried to combine different classifiers.
5. I couldn’t get glm work so I used rf, gbm and lda.
6. Training of GBM model takes a lot of processing power and I tried using the doParallel package to speed up.
7. Results of GBM and LDA were disappointing and the combined model was not good.
8. Then, I try to fit a few  random forest with different number of trees, I found the results quite similar with trees = 200,600 & 1000.
9. I tried to use GAM to ensemble them but the result was very poor.
**Codes and results of Step 4-9 are not shown here.*
10. Finally, I tried to add more features and accuracy jumped to 0.99.
```{r more}
magnet<-grep("^magnet",names(data))
yaw<-grep("^yaw",names(data))
pitch<-grep("^pitch",names(data))
roll<-grep("^roll",names(data))
select_feature<-c(gyros,accel,magnet,yaw,pitch,roll,160) # with the outcome
training <- data[inTrain,select_feature]
testing <- data[-inTrain,select_feature]
case<-case[,select_feature]
# Fit model using random forrest
modelFit<-randomForest(classe~.,method="rf",data=training)
# Valid the model with the testing data
confusionMatrix(testing$classe,predict(modelFit,testing))$overall[1]
```
11. Using the fitted model to predict the 20 test cases
```{r predict}
predict(modelFit,case)
```